---
title: "filling_the_gap dealing the NA"
author: "Haozhe Wang"
date: '2022-08-06'
output: pdf_document
---


This is the first code markdown file.This file try to deal with the missing values.


set the path, the path in which file contains the data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
path <- "C:/Users/whz/Desktop/res/Edingburgh/disseration/Project 2/data/SDS_Project_2022_FillingTheGap"
setwd(path )
print.all.code=TRUE
```


 


# call the library
```{r}
library(sp)
library(rgdal)
library(raster)
library(ggplot2)
library(viridis)
library(rasterVis)
library(ambient)
memory.limit(24000)
```





# load the data change to rastor type

First load the data by raster type. Data 1-6 in Sentinel-2 used UTM, but Sentinel-1 using longlat. So I change UTM to longlat. By the way the region of sentinel-2 and sentinel-1 is not exactly same. Therefore, I reprojection s2 to s1 to make sure them cover the same region.

```{r}
# Load data S1
s1_aoi_1_brick <- brick(paste0(path, "/s1/s1_aoi_1.tif"))
s1_aoi_2_brick <- brick(paste0(path, "/s1/s1_aoi_2.tif"))
s1_aoi_3_brick <- brick(paste0(path, "/s1/s1_aoi_3.tif"))
s1_aoi_4_brick <- brick(paste0(path, "/s1/s1_aoi_4.tif"))
s1_aoi_5_brick <- brick(paste0(path, "/s1/s1_aoi_5.tif"))
s1_aoi_6_brick <- brick(paste0(path, "/s1/s1_aoi_6.tif"))
s1_aoi_7_brick <- brick(paste0(path, "/s1/s1_aoi_7.tif"))
s1_aoi_8_brick <- brick(paste0(path, "/s1/s1_aoi_8.tif"))
s1_aoi_9_brick <- brick(paste0(path, "/s1/s1_aoi_9.tif"))
s1_aoi_10_brick <- brick(paste0(path, "/s1/s1_aoi_10.tif"))

# Load data S2
s2_aoi_1_brick <- brick(paste0(path, "/s2/s2_aoi_1.tif"))
s2_aoi_2_brick <- brick(paste0(path, "/s2/s2_aoi_2.tif"))
s2_aoi_3_brick <- brick(paste0(path, "/s2/s2_aoi_3.tif"))
s2_aoi_4_brick <- brick(paste0(path, "/s2/s2_aoi_4.tif"))
s2_aoi_5_brick <- brick(paste0(path, "/s2/s2_aoi_5.tif"))
s2_aoi_6_brick <- brick(paste0(path, "/s2/s2_aoi_6.tif"))
s2_aoi_7_brick <- brick(paste0(path, "/s2/s2_aoi_7.tif"))
s2_aoi_8_brick <- brick(paste0(path, "/s2/s2_aoi_8.tif"))
s2_aoi_9_brick <- brick(paste0(path, "/s2/s2_aoi_9.tif"))
s2_aoi_10_brick <- brick(paste0(path, "/s2/s2_aoi_10.tif"))


# figure 1,2,3,4,5 and 6 are using UTM we need to change to longlat
# The sentinel-2's band are red blue green and NIR. Their values are integer.
# So I choose ngb method to keep the value are integer.
s2_aoi_1_brick <- projectRaster(s2_aoi_1_brick, s1_aoi_1_brick, 
         crs="+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs ",method="ngb")
s2_aoi_2_brick <- projectRaster(s2_aoi_2_brick, s1_aoi_2_brick, 
         crs="+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs ",method="ngb")
s2_aoi_3_brick <- projectRaster(s2_aoi_3_brick, s1_aoi_3_brick, 
         crs="+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs ",method="ngb")
s2_aoi_4_brick <- projectRaster(s2_aoi_4_brick, s1_aoi_4_brick, 
         crs="+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs ",method="ngb")
s2_aoi_5_brick <- projectRaster(s2_aoi_5_brick, s1_aoi_5_brick, 
         crs="+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs ",method="ngb")
s2_aoi_6_brick <- projectRaster(s2_aoi_6_brick, s1_aoi_6_brick, 
         crs="+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs ",method="ngb")



names(s2_aoi_1_brick) <- c("blue","green","red","NIR")
names(s2_aoi_2_brick) <- c("blue","green","red","NIR")
names(s2_aoi_3_brick) <- c("blue","green","red","NIR")
names(s2_aoi_4_brick) <- c("blue","green","red","NIR")
names(s2_aoi_5_brick) <- c("blue","green","red","NIR")
names(s2_aoi_6_brick) <- c("blue","green","red","NIR")
names(s2_aoi_7_brick) <- c("blue","green","red","NIR")
names(s2_aoi_8_brick) <- c("blue","green","red","NIR")
names(s2_aoi_9_brick) <- c("blue","green","red","NIR")
names(s2_aoi_10_brick) <- c("blue","green","red","NIR")

```







# set NA (if all four band is 0 for sentinel 2 then chage to NA)


In sentinel-2, If all four bands' values are 0 we need to set to NA.
```{r}
#if all four band is 0 for sentinel 2 then chage to NA

# the set NA function
setNA <- function(x){
  index <- which(rowSums(x[,3:6]) ==0)
  x[index,3:6]<- NA
  x
}



# figure 1

crs <- s2_aoi_1_brick@crs # load the old crs
s2_aoi_1_brick_matrix <-as.data.frame(s2_aoi_1_brick , xy = T) # change to dataframe
s2_aoi_1_brick_matrix <- setNA (s2_aoi_1_brick_matrix) # set NA
s2_aoi_1_brick <- rasterFromXYZ(s2_aoi_1_brick_matrix,crs=crs) # change back to brick

# figure 2

crs <- s2_aoi_2_brick@crs # load the old crs
s2_aoi_2_brick_matrix <-as.data.frame(s2_aoi_2_brick , xy = T) # change to dataframe
s2_aoi_2_brick_matrix <- setNA (s2_aoi_2_brick_matrix) # set NA
s2_aoi_2_brick <- rasterFromXYZ(s2_aoi_2_brick_matrix,crs=crs)# change back to brick


# figure 3

crs <- s2_aoi_3_brick@crs # load the old crs
s2_aoi_3_brick_matrix <-as.data.frame(s2_aoi_3_brick , xy = T) # change to dataframe
s2_aoi_3_brick_matrix <- setNA (s2_aoi_3_brick_matrix) # set NA
s2_aoi_3_brick <- rasterFromXYZ(s2_aoi_3_brick_matrix,crs=crs) # change back to brick


# figure 4

crs <- s2_aoi_4_brick@crs # load the old crs
s2_aoi_4_brick_matrix <-as.data.frame(s2_aoi_4_brick , xy = T) # change to dataframe
s2_aoi_4_brick_matrix <- setNA (s2_aoi_4_brick_matrix) # set NA
s2_aoi_4_brick <- rasterFromXYZ(s2_aoi_4_brick_matrix,crs=crs) # change back to brick


#
#I find the figure 5,6,7,8,9 and 10 is too large to using rasterFromXYZ generate the brick
# so I do it separately 
# first generate the each layer then combine as a brick


# figure 5
crs <- s2_aoi_5_brick@crs # load the old crs
s2_aoi_5_brick_matrix <-as.data.frame(s2_aoi_5_brick , xy = T) # change to dataframe
s2_aoi_5_brick_matrix <- setNA (s2_aoi_5_brick_matrix) # set NA
s2_aoi_5_brick[[1]] <- rasterFromXYZ(s2_aoi_5_brick_matrix[,1:3],crs=crs) # change back to stack
s2_aoi_5_brick[[2]] <- rasterFromXYZ(s2_aoi_5_brick_matrix[,c(1,2,4)],crs=crs) # change back to stack
s2_aoi_5_brick[[3]] <- rasterFromXYZ(s2_aoi_5_brick_matrix[,c(1,2,5)],crs=crs) # change back to stack
s2_aoi_5_brick[[4]] <- rasterFromXYZ(s2_aoi_5_brick_matrix[,c(1,2,6)],crs=crs) # change back to stack
s2_aoi_5_brick <- brick(s2_aoi_5_brick) # change back to brick


# figure 6
crs <- s2_aoi_6_brick@crs # load the old crs
s2_aoi_6_brick_matrix <-as.data.frame(s2_aoi_6_brick , xy = T) # change to dataframe
s2_aoi_6_brick_matrix <- setNA (s2_aoi_6_brick_matrix) # set NA
s2_aoi_6_brick[[1]] <- rasterFromXYZ(s2_aoi_6_brick_matrix[,1:3],crs=crs) # change back to brick
s2_aoi_6_brick[[2]] <- rasterFromXYZ(s2_aoi_6_brick_matrix[,c(1,2,4)],crs=crs) # change back to brick
s2_aoi_6_brick[[3]] <- rasterFromXYZ(s2_aoi_6_brick_matrix[,c(1,2,5)],crs=crs) # change back to brick
s2_aoi_6_brick[[4]] <- rasterFromXYZ(s2_aoi_6_brick_matrix[,c(1,2,6)],crs=crs) # change back to brick
s2_aoi_6_brick <- brick(s2_aoi_6_brick) # change back to brick



# figure 7
crs <- s2_aoi_7_brick@crs # load the old crs
s2_aoi_7_brick_matrix <-as.data.frame(s2_aoi_7_brick , xy = T) # change to dataframe
s2_aoi_7_brick_matrix <- setNA (s2_aoi_7_brick_matrix) # set NA
s2_aoi_7_brick[[1]] <- rasterFromXYZ(s2_aoi_7_brick_matrix[,1:3],crs=crs) # change back to brick
s2_aoi_7_brick[[2]] <- rasterFromXYZ(s2_aoi_7_brick_matrix[,c(1,2,4)],crs=crs) # change back to brick
s2_aoi_7_brick[[3]] <- rasterFromXYZ(s2_aoi_7_brick_matrix[,c(1,2,5)],crs=crs) # change back to brick
s2_aoi_7_brick[[4]] <- rasterFromXYZ(s2_aoi_7_brick_matrix[,c(1,2,6)],crs=crs) # change back to brick
s2_aoi_7_brick <- brick(s2_aoi_7_brick) # change back to brick

# figure 8
crs <- s2_aoi_8_brick@crs # load the old crs
s2_aoi_8_brick_matrix <-as.data.frame(s2_aoi_8_brick , xy = T) # change to dataframe
s2_aoi_8_brick_matrix <- setNA (s2_aoi_8_brick_matrix) # set NA
s2_aoi_8_brick[[1]] <- rasterFromXYZ(s2_aoi_8_brick_matrix[,1:3],crs=crs) # change back to brick
s2_aoi_8_brick[[2]] <- rasterFromXYZ(s2_aoi_8_brick_matrix[,c(1,2,4)],crs=crs) # change back to brick
s2_aoi_8_brick[[3]] <- rasterFromXYZ(s2_aoi_8_brick_matrix[,c(1,2,5)],crs=crs) # change back to brick
s2_aoi_8_brick[[4]] <- rasterFromXYZ(s2_aoi_8_brick_matrix[,c(1,2,6)],crs=crs) # change back to brick
s2_aoi_8_brick <- brick(s2_aoi_8_brick) # change back to brick


# figure 9 and 10 do not contains all four bands are 0

s2_aoi_9_brick_matrix <-as.data.frame(s2_aoi_9_brick , xy = T) # change to dataframe
which(rowSums(s2_aoi_9_brick_matrix[,3:6]) ==0)
which(is.na(s2_aoi_9_brick_matrix))

s2_aoi_10_brick_matrix <-as.data.frame(s2_aoi_10_brick , xy = T) # change to dataframe
which(rowSums(s2_aoi_10_brick_matrix[,3:6]) ==0)
which(is.na(s2_aoi_10_brick_matrix))


```

# see the pattern of NA

After we set the NA in Sentinel-2, let us see the pattern of the missing values.
```{r}

# pattern of NA for Sentinel 2
# figure 1 
plot(s2_aoi_1_brick_matrix[which(is.na(s2_aoi_1_brick_matrix[,3])),1],
     s2_aoi_1_brick_matrix[which(is.na(s2_aoi_1_brick_matrix[,3])),2],
     main="Sentinel 2 figure 1,  NA pattern", xlab="Longitude", ylab="Latitude",
     xlim=s2_aoi_1_brick@extent[1:2],ylim=s2_aoi_1_brick@extent[3:4])

# figure 2 
plot(s2_aoi_2_brick_matrix[which(is.na(s2_aoi_2_brick_matrix[,3])),1],
     s2_aoi_2_brick_matrix[which(is.na(s2_aoi_2_brick_matrix[,3])),2],
     main="Sentinel 2 figure 2,  NA pattern", xlab="Longitude", ylab="Latitude",
     xlim=s2_aoi_2_brick@extent[1:2],ylim=s2_aoi_2_brick@extent[3:4])

# figure 3
plot(s2_aoi_3_brick_matrix[which(is.na(s2_aoi_3_brick_matrix[,3])),1],
     s2_aoi_3_brick_matrix[which(is.na(s2_aoi_3_brick_matrix[,3])),2],
     main="Sentinel 2 figure 3,  NA pattern", xlab="Longitude", ylab="Latitude",
     xlim=s2_aoi_3_brick@extent[1:2],ylim=s2_aoi_3_brick@extent[3:4])

# figure 4 
plot(s2_aoi_4_brick_matrix[which(is.na(s2_aoi_4_brick_matrix[,3])),1],
     s2_aoi_4_brick_matrix[which(is.na(s2_aoi_4_brick_matrix[,3])),2],
     main="Sentinel 2 figure 4,  NA pattern", xlab="Longitude", ylab="Latitude",
     xlim=s2_aoi_4_brick@extent[1:2],ylim=s2_aoi_4_brick@extent[3:4])

# figure 5 
plot(s2_aoi_5_brick_matrix[which(is.na(s2_aoi_5_brick_matrix[,3])),1],
     s2_aoi_5_brick_matrix[which(is.na(s2_aoi_5_brick_matrix[,3])),2],
     main="Sentinel 2 figure 5,  NA pattern", xlab="Longitude", ylab="Latitude",
     xlim=s2_aoi_5_brick@extent[1:2],ylim=s2_aoi_5_brick@extent[3:4])


# figure 6 
plot(s2_aoi_6_brick_matrix[which(is.na(s2_aoi_6_brick_matrix[,3])),1],
     s2_aoi_6_brick_matrix[which(is.na(s2_aoi_6_brick_matrix[,3])),2],
     main="Sentinel 2 figure 6,  NA pattern", xlab="Longitude", ylab="Latitude",
     xlim=s2_aoi_6_brick@extent[1:2],ylim=s2_aoi_6_brick@extent[3:4])

# figure 7 
plot(s2_aoi_7_brick_matrix[which(is.na(s2_aoi_7_brick_matrix[,3])),1],
     s2_aoi_7_brick_matrix[which(is.na(s2_aoi_7_brick_matrix[,3])),2],
     main="Sentinel 2 figure 7,  NA pattern", xlab="Longitude", ylab="Latitude",
     xlim=s2_aoi_7_brick@extent[1:2],ylim=s2_aoi_7_brick@extent[3:4])

# figure 8 
plot(s2_aoi_8_brick_matrix[which(is.na(s2_aoi_8_brick_matrix[,3])),1],
     s2_aoi_8_brick_matrix[which(is.na(s2_aoi_8_brick_matrix[,3])),2],
     main="Sentinel 2 figure 8,  NA pattern", xlab="Longitude", ylab="Latitude",
     xlim=s2_aoi_8_brick@extent[1:2],ylim=s2_aoi_8_brick@extent[3:4])

```

# remove the na 

From above plot, we know data 9, 10 do not contains NA in sentinel-2. Data 7 has missing value in the center of the plot. The others only have missing values in the edges of the figure. So I cut the edge to remove the missing values. However, We also need to check the Sentinel-1 data. There are missing values contain in data 5 7 and 10. The missingness are in the center of the figure, so I imputed the missing values by the mean value of its around pixels. 
```{r}
# we only need to drop the pictures' four sides
# the centre of the pictures do not contain NA

# figure 1
s2_aoi_1_brick@extent
# base on the plot we can set x >= -7.56
# base on the plot we can set x <= -7.019256 
# base on the plot we can set y >= 37.87 
# base on the plot we can set y <= 38.31 
extent <- s2_aoi_1_brick@extent
extent[1:4] <- c(-7.56,-7.019256,37.87,38.31) # set new extent
s2_aoi_1_brick <- crop(s2_aoi_1_brick,extent)
s2_aoi_1_brick_matrix <- as.data.frame(s2_aoi_1_brick, xy=T)
which(is.na(s2_aoi_1_brick_matrix)) # check whether matrix contains na 
s1_aoi_1_brick <- crop(s1_aoi_1_brick,extent)
s1_aoi_1_brick_matrix <- as.data.frame(s1_aoi_1_brick, xy=T)
which(is.na(s1_aoi_1_brick_matrix)) # check whether matrix contains na 



# figure 2

s2_aoi_2_brick@extent
# base on the plot we can set x >= -7.435715 
# base on the plot we can set x <= -7.07
# base on the plot we can set y >= 38.37
# base on the plot we can set y <= 38.80

extent <- s2_aoi_2_brick@extent
extent[1:4] <- c(-7.435715 ,-7.07,38.37,38.80)# set new extent
s2_aoi_2_brick <- crop(s2_aoi_2_brick,extent)
s2_aoi_2_brick_matrix <- as.data.frame(s2_aoi_2_brick, xy=T)
which(is.na(s2_aoi_2_brick_matrix)) # check whether matrix contains na 
s1_aoi_2_brick <- crop(s1_aoi_2_brick,extent)
s1_aoi_2_brick_matrix <- as.data.frame(s1_aoi_2_brick, xy=T)
which(is.na(s1_aoi_2_brick_matrix)) # check whether matrix contains na 




# figure 3
s2_aoi_3_brick@extent
# base on the plot we can set x >= -6.966076 
# base on the plot we can set x <=  -6.63
# base on the plot we can set y >= 38.44
# base on the plot we can set y <= 38.80



extent <- s2_aoi_3_brick@extent
extent[1:4] <- c(-6.966076,-6.63,38.44,38.80) # set new extent
s2_aoi_3_brick <- crop(s2_aoi_3_brick,extent) # crop 
s2_aoi_3_brick_matrix <- as.data.frame(s2_aoi_3_brick, xy=T)
which(is.na(s2_aoi_3_brick_matrix)) # check whether matrix contains na 
s1_aoi_3_brick <- crop(s1_aoi_3_brick,extent)
s1_aoi_3_brick_matrix <- as.data.frame(s1_aoi_3_brick, xy=T)
which(is.na(s1_aoi_3_brick_matrix)) # check whether matrix contains na 




# figure 4

s2_aoi_4_brick@extent
# base on the plot we can set x >= -6.93
# base on the plot we can set x <= -6.631004 
# base on the plot we can set y >= 38.10258 
# base on the plot we can set y <= 38.4046 

extent <- s2_aoi_4_brick@extent
extent[1:4] <- c(-6.93,-6.631004 ,38.10258 ,38.4046 ) # set new extent
s2_aoi_4_brick <- crop(s2_aoi_4_brick,extent) # crop 
s2_aoi_4_brick_matrix <- as.data.frame(s2_aoi_4_brick, xy=T)
which(is.na(s2_aoi_4_brick_matrix)) # check whether matrix contains na 
s1_aoi_4_brick <- crop(s1_aoi_4_brick,extent)
s1_aoi_4_brick_matrix <- as.data.frame(s1_aoi_4_brick, xy=T)
which(is.na(s1_aoi_4_brick_matrix)) # check whether matrix contains na 





# figure 5
s2_aoi_5_brick@extent
# base on the plot we can set x >=  -8.95
# base on the plot we can set x <= -7.44
# base on the plot we can set y >= 52.2762 
# base on the plot we can set y <= 52.73


extent <- s2_aoi_5_brick@extent
extent[1:4] <- c(-8.95,-7.44 ,52.2762  ,52.73 ) # set new extent
s2_aoi_5_brick <- crop(s2_aoi_5_brick,extent) # crop 
s2_aoi_5_brick_matrix <- as.data.frame(s2_aoi_5_brick, xy=T)
which(is.na(s2_aoi_5_brick_matrix)) # check whether matrix contains na 
s1_aoi_5_brick <- crop(s1_aoi_5_brick,extent)
s1_aoi_5_brick_matrix <- as.data.frame(s1_aoi_5_brick, xy=T)
which(is.na(s1_aoi_5_brick_matrix)) # check whether matrix contains na 

# there is NA in sentinel 1
# figure 5 of sentinel 1
plot(s1_aoi_5_brick_matrix[which(is.na(s1_aoi_5_brick_matrix[,3])),1],
     s1_aoi_5_brick_matrix[which(is.na(s1_aoi_5_brick_matrix[,3])),2],
     col = 2, pch = 19,xlim=s2_aoi_5_brick@extent[1:2],ylim=s2_aoi_5_brick@extent[3:4],
     xlab="Longitude", ylab="Latitude")
# the missing is occur in particular terrain 

imputed_1 <-function(x){
  index <- which(is.na(x[,3]))
  a<-0.0001796631
  for (i in index){
    xlim <- x[i,1]
    ylim <- x[i,2]
    index_2 <- which(x[,1]<=xlim+2*a&x[,1]>=xlim-2*a&x[,2]<=ylim+2*a&x[,2]>=ylim-2*a)
    x[i,3]<- mean(x[index_2,3],na.rm=TRUE)
    x[i,4]<- mean(x[index_2,4],na.rm=TRUE)
  }
  x
}

s1_aoi_5_brick_matrix <- imputed_1(s1_aoi_5_brick_matrix)

# figure 6

s2_aoi_6_brick@extent
# base on the plot we can set x >= -8.9686 
# base on the plot we can set x <= -7.386487 
# base on the plot we can set y >= 52.77602 
# base on the plot we can set y <= 53.23



extent <- s2_aoi_6_brick@extent
extent[1:4] <- c(-8.9686 ,-7.386487  ,52.77602  ,53.23 ) # set new extent
s2_aoi_6_brick <- crop(s2_aoi_6_brick,extent) # crop 
s2_aoi_6_brick_matrix <- as.data.frame(s2_aoi_6_brick, xy=T)
which(is.na(s2_aoi_6_brick_matrix)) # check whether matrix contains na 
s1_aoi_6_brick <- crop(s1_aoi_6_brick,extent)
s1_aoi_6_brick_matrix <- as.data.frame(s1_aoi_6_brick, xy=T)
which(is.na(s1_aoi_6_brick_matrix)) # check whether matrix contains na 





# figure 7

s2_aoi_7_brick@extent
# base on the plot we can set x >= -122.9571 
# base on the plot we can set x <= -121.74 
# base on the plot we can set y >= 39.075
# base on the plot we can set y <= 39.72009 

# there is NA pattern  not the edge anymore
# figure 7 of sentinel 2
plot(s2_aoi_7_brick_matrix[which(is.na(s2_aoi_7_brick_matrix[,3])),1],
     s2_aoi_7_brick_matrix[which(is.na(s2_aoi_7_brick_matrix[,3])),2],
     col = "blue", pch = 19,xlim=s2_aoi_7_brick@extent[1:2],ylim=s2_aoi_7_brick@extent[3:4],
      xlab="Longitude", ylab="Latitude")
s1_aoi_7_brick_matrix <- as.data.frame(s1_aoi_7_brick,xy=T)
points(s1_aoi_7_brick_matrix[which(is.na(s1_aoi_7_brick_matrix[,3])),1],
     s1_aoi_7_brick_matrix[which(is.na(s1_aoi_7_brick_matrix[,3])),2],
     col = "green", pch = 19)
# the missing is occur in particular terrain 

# there are too many missing values ,so we do not cut the figure
# we can leave the NA
# we can impute base on the neighborhood


s1_aoi_7_brick_matrix <- imputed_1(s1_aoi_7_brick_matrix)


imputed_2 <-function(x){
  index <- which(is.na(x[,3]))
  a<-0.0001796631
  for (i in index){
    xlim <- x[i,1]
    ylim <- x[i,2]
    index_2 <- which(x[,1]<=xlim+2*a&x[,1]>=xlim-2*a&x[,2]<=ylim+2*a&x[,2]>=ylim-2*a)
    x[i,3]<- mean(x[index_2 ,3],na.rm=TRUE)
    x[i,4]<- mean(x[index_2 ,4],na.rm=TRUE)
    x[i,5]<- mean(x[index_2 ,5],na.rm=TRUE)
    x[i,6]<- mean(x[index_2 ,6],na.rm=TRUE)
  }
  x
}

s2_aoi_7_brick_matrix <- imputed_2(s2_aoi_7_brick_matrix)
# figure 8

s2_aoi_8_brick@extent
# base on the plot we can set x >= -65.21
# base on the plot we can set x <= -64.166 
# base on the plot we can set y >= -37.101
# base on the plot we can set y <= -36.16653 



extent <- s2_aoi_8_brick@extent
extent[1:4] <- c(-65.21 ,-64.166   ,-37.101  ,-36.16653 ) # set new extent
s2_aoi_8_brick <- crop(s2_aoi_8_brick,extent) # crop 
s2_aoi_8_brick_matrix <- as.data.frame(s2_aoi_8_brick, xy=T)
which(is.na(s2_aoi_8_brick_matrix)) # check whether matrix contains na 
s1_aoi_8_brick <- crop(s1_aoi_8_brick,extent)
s1_aoi_8_brick_matrix <- as.data.frame(s1_aoi_8_brick, xy=T)
which(is.na(s1_aoi_8_brick_matrix)) # check whether matrix contains na 








# figure 9 
s1_aoi_9_brick_matrix <- as.data.frame(s1_aoi_9_brick,xy=T)
which(is.na(s1_aoi_9_brick_matrix))


# figure 10
s1_aoi_10_brick_matrix <- as.data.frame(s1_aoi_10_brick,xy=T)
which(is.na(s1_aoi_10_brick_matrix))


plot(s1_aoi_10_brick_matrix[which(is.na(s1_aoi_10_brick_matrix[,3])),1],
     s1_aoi_10_brick_matrix[which(is.na(s1_aoi_10_brick_matrix[,3])),2],
     col = "blue", pch = 19,xlim=s2_aoi_10_brick@extent[1:2],ylim=s2_aoi_10_brick@extent[3:4], 
     xlab="Longitude", ylab="Latitude")

s1_aoi_10_brick_matrix <- imputed_1(s1_aoi_10_brick_matrix)
```


# save the new rastor 


save the preprocessing raster for convenience and further work.
```{r}
# figure 1
# save the tif
writeRaster(x = s1_aoi_1_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_1_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif


# save the tif
writeRaster(x = s2_aoi_1_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s2/s2_aoi_1_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif


# figure 2
# save the tif
writeRaster(x = s1_aoi_2_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_2_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif


# save the tif
writeRaster(x = s2_aoi_2_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s2/s2_aoi_2_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif

# figure 3
# save the tif
writeRaster(x = s1_aoi_3_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_3_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif


# save the tif
writeRaster(x = s2_aoi_3_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s2/s2_aoi_3_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif

# figure 4
# save the tif
writeRaster(x = s1_aoi_4_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_4_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif


# save the tif
writeRaster(x = s2_aoi_4_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s2/s2_aoi_4_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif


# figure 5
# save the tif
writeRaster(x = s1_aoi_5_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_5_brick_1_1.tif"), 	
            format = "GTiff") 					# save as a tif



# save the tif
writeRaster(x = s2_aoi_5_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s2/s2_aoi_5_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif



# figure 6
# save the tif
writeRaster(x = s1_aoi_6_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_6_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif


# save the tif
writeRaster(x = s2_aoi_6_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s2/s2_aoi_6_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif

# figure 7
# save the tif
writeRaster(x = s1_aoi_7_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_7_brick_1_1.tif"), 	
            format = "GTiff") 					# save as a tif


# save the tif
writeRaster(x = s2_aoi_7_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s2/s2_aoi_7_brick_1_1.tif"), 	
            format = "GTiff") 					# save as a tif


# figure 8
# save the tif
writeRaster(x = s1_aoi_8_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_8_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif


# save the tif
writeRaster(x = s2_aoi_8_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s2/s2_aoi_8_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif


# figure 9
# save the tif
writeRaster(x = s1_aoi_9_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_9_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif


# save the tif
writeRaster(x = s2_aoi_9_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s2/s2_aoi_9_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif



# figure 10
# save the tif
writeRaster(x = s1_aoi_10_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_10_brick_1_1.tif"), 	
            format = "GTiff") 					# save as a tif





# save the tif
writeRaster(x = s2_aoi_10_brick,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s2/s2_aoi_10_brick_1.tif"), 	
            format = "GTiff") 					# save as a tif
```









```{r}
# figure 5
crs <- s1_aoi_5_brick@crs # load the old crs
s1_aoi_5_brick_1 <- rasterFromXYZ(s1_aoi_5_brick_matrix[,1:3],crs=crs) # change back to raster
s1_aoi_5_brick_2 <- rasterFromXYZ(s1_aoi_5_brick_matrix[,c(1,2,4)],crs=crs) # change back to raster
s1_aoi_5_brick_3 <- rasterFromXYZ(s1_aoi_5_brick_matrix[,c(1,2,5)],crs=crs) # change back to raster
s1_aoi_5_brick_ <- brick(s1_aoi_5_brick_1,s1_aoi_5_brick_2,s1_aoi_5_brick_3)
names(s1_aoi_5_brick_) <- c("VV","VH","angle")
# save the tif
writeRaster(x = s1_aoi_5_brick_,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_5_brick_1_2.tif"), 	
            format = "GTiff") 					# save as a tif

# figure 7

crs <- s1_aoi_7_brick@crs # load the old crs
s1_aoi_7_brick_1 <- rasterFromXYZ(s1_aoi_7_brick_matrix[,1:3],crs=crs) # change back to raster
s1_aoi_7_brick_2 <- rasterFromXYZ(s1_aoi_7_brick_matrix[,c(1,2,4)],crs=crs) # change back to raster
s1_aoi_7_brick_3 <- rasterFromXYZ(s1_aoi_7_brick_matrix[,c(1,2,5)],crs=crs) # change back to raster
s1_aoi_7_brick_ <- brick(s1_aoi_7_brick_1,s1_aoi_7_brick_2,s1_aoi_7_brick_3)
names(s1_aoi_7_brick_) <- c("VV","VH","angle")
# save the tif
writeRaster(x = s1_aoi_7_brick_,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_7_brick_1_2.tif"), 	
            format = "GTiff") 					# save as a tif


crs <- s2_aoi_7_brick@crs # load the old crs
s2_aoi_7_brick_1 <- rasterFromXYZ(s2_aoi_7_brick_matrix[,1:3],crs=crs) # change back to raster
s2_aoi_7_brick_2 <- rasterFromXYZ(s2_aoi_7_brick_matrix[,c(1,2,4)],crs=crs) # change back to raster
s2_aoi_7_brick_3 <- rasterFromXYZ(s2_aoi_7_brick_matrix[,c(1,2,5)],crs=crs) # change back to raster
s2_aoi_7_brick_4 <- rasterFromXYZ(s2_aoi_7_brick_matrix[,c(1,2,6)],crs=crs) # change back to raster
s2_aoi_7_brick_ <- brick(s2_aoi_7_brick_1,s2_aoi_7_brick_2,s2_aoi_7_brick_3,s2_aoi_7_brick_4)
names(s2_aoi_7_brick_) <- c("blue","green","red","NIR")

# save the tif
writeRaster(x = s2_aoi_7_brick_,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s2/s2_aoi_7_brick_1_2.tif"), 	
            format = "GTiff") 					# save as a tif

# figure 10
crs <- s1_aoi_10_brick@crs # load the old crs
s1_aoi_10_brick_1 <- rasterFromXYZ(s1_aoi_10_brick_matrix[,1:3],crs=crs) # change back to raster
s1_aoi_10_brick_2 <- rasterFromXYZ(s1_aoi_10_brick_matrix[,c(1,2,4)],crs=crs) # change back to raster
s1_aoi_10_brick_3 <- rasterFromXYZ(s1_aoi_10_brick_matrix[,c(1,2,5)],crs=crs) # change back to raster
s1_aoi_10_brick_ <- brick(s1_aoi_10_brick_1,s1_aoi_10_brick_2,s1_aoi_10_brick_3)
names(s1_aoi_10_brick_) <- c("VV","VH","angle")
# save the tif
writeRaster(x = s1_aoi_10_brick_,

            # where your file will go - update with your file path!
	    
            filename=paste0(path, "/s1/s1_aoi_10_brick_1_2.tif"), 	
            format = "GTiff") 					# save as a tif

```











